---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "Readme_files/"
)

library(rmmodeldata)
```

# rmmodeldata: Remove data from models

## Overview

Building models is an essential skill for scientists or practioneers when working with data. In some research areas, such as it is for medical data, contains sensitive information which should not get shared. However, most `R` models, such as `lm`, contains the original data used for training the model.

This package provides mechanisms to train algorithms without storing the data or removing model data from a model. For simpler model objects (e.g. `lm`) it is sufficient to remove parts from the object to ensure privacy. More complex algorithms (e.g. `partykit::cforest`), on the other side, requires adaptions of the fitting and prediction algorithm to provide full privacy and functionality without storing data.

The functions you get by installing this package are:
- A generic `rmdata` method for simpler models to just remove data
- Functions to train and predict more complex models. Available algorithms:
  - `cforest`
  - `traforest`

Using a more complex function overwrites the original one and returns the same object with a suffix `.nodata`. For example, training a model using `partykit::cforest` returns an object of class `cforest.nodata`. For this class, special predict methods are implemented and used instead of the original `partykit:::predict.cforest` method.

## Search for values (WIP)

In order to detect data in an `R` object, `rmmodeldata` provides a function `searchObjectForValue` which searches through an object for a specific value.

__Examples:__

```{r}
vfound = searchObjectForValue(iris, iris[100, 2])
cat(vfound$found, sep = "\n")
```

```{r}
mod = lm(Sepal.Length ~ ., data = iris)
vfound = searchObjectForValue(mod, iris[100, 2])
cat(vfound$found, sep = "\n")
```

## Disclaimer

It is suggested to use the namespace `rmmodeldata` for calling functions to ensure the usage of the correct method. A message is printed when a method of `rmmodeldata` is used. Otherwise, it cannot be distinguished between the original and the new method.


## Installation

#### Developer version:

```r
remotes::install_github("difuture-lmu/rmmodeldata")
```

## Example

```{r}
set.seed(31415)
idx_train = sample(x = c(TRUE, FALSE), size = nrow(iris), replace = TRUE, prob = c(0.8, 0.2))

dat_train = iris[idx_train, ]
dat_test  = iris[! idx_train, ]

set.seed(31415)
mod_without_data = rmmodeldata::cforest(Petal.Length ~ ., data = dat_train)
pred_without_data = predict(mod_without_data, newdata = dat_test)

str(pred_without_data)
```
