---
title: "Train cforest without storing data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Train cforest without storing data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rmmodeldata)
```

## Simulate Data

```{r}
simData = function(n = 500, p = 10, beta = 3, sd = 1) {

  ## treatment
  lev = LETTERS[1:4]
  a = factor(sample(lev, n, TRUE), labels = lev, levels = lev)

  ## correlated z variables
  sigma = diag(p)
  sigma[sigma == 0] = 0.2
  ztemp = mvtnorm::rmvnorm(n, sigma = sigma)
  z = (pnorm(ztemp) * 2 * pi) - pi
  colnames(z) = paste0("z", 1:ncol(z))
  z1 = z[,1]

  ## outcome
  y = 7 + 0.2 * (a %in% "A") + beta * cos(z1) * (a %in% "A") + rnorm(n, 0, sd)

  data.frame(y = y, a = a, z)
}

beta     = 3
p        = 5
ntrain   = 500
ntest    = 20

set.seed(31415)
simdata = simData(p, beta, ntrain)

set.seed(31415)
tsimdata = simData(p, beta, ntest)
```

## Compare cforest with and without data

Train the random forests. The first forest `mod_with_data` is the object returned by the original `cforest` function from `partykit`. The second forest object `mod_without_data` is the one returned without data from `rmmodeldata`.

```{r}
set.seed(31415)
mod_with_data = partykit::cforest(y ~ ., data = simdata)

set.seed(31415)
mod_without_data = cforest(y ~ ., data = simdata)
```

Now we want to compare the predictions returned from the objects. Note that due to namespace clashes when using `partykit` functionality via the namespace, we also export every predict function as non generic method with a prefix `predict_`. Hence, the save way to call the correct predict method is to use `predict_cforest`:

```{r}
pred_with_data = partykit::predict.cforest(mod_with_data, newdata = tsimdata)

pred_without_data = predict(mod_without_data, newdata = tsimdata)
# same as:
pred_without_data = rmmodeldata:::predict.cforest.nodata(mod_without_data, newdata = tsimdata)

all.equal(pred_with_data, pred_without_data)
```

Note: The generic `predict.cforest` is also exported but can be overloaded by partykit.


## Check if a value from the data set can be found in the model structure

```{r}
lfound_with_data = searchObjectForValue(mod_with_data, simdata[1, 1])
cat(lfound_with_data$found, sep = "\n")

lfound_without_data = searchObjectForValue(mod_without_data, simdata[1, 1])
cat(lfound_without_data$found, sep = "\n")
```
