---
title: "traforest"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{traforest}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)
```

## Load packages

```{r setup}
library(rmmodeldata)
library(trtf)
library(survival)
```

## Use case

The used data is directly copied from the manual page `?traforest` of `traforest`. The main purpose is to test and to show if removing the data gives equal predictions.

## Used data set

```{r}
### German Breast Cancer Study Group 2 data set
data("GBSG2", package = "TH.data")
```

```{r, echo=FALSE}
knitr::kable(head(GBSG2))
```

## Preparation for traforest

Set-up Cox model with overall treatment effect in hormonal therapy

```{r}
yvar = numeric_var("y", support = c(100, 2000), bounds = c(0, Inf))
By = Bernstein_basis(yvar, order = 5, ui = "incre")
m = ctm(response = By, shifting = ~ horTh, todistr = "MinExt", data = GBSG2)
GBSG2$y = with(GBSG2, Surv(time, cens))

### estimate age-dependent Cox models (here ignoring all other covariates)
ctrl = ctree_control(minsplit = 50, minbucket = 20, mincriterion = 0)
```

Train `traforest` from `trtf`:

```{r}
set.seed(290875)
tf_cmod = trtf::traforest(m, formula = y ~ horTh | age, control = ctrl,
  ntree = 50, mtry = 1, trace = TRUE, data = GBSG2)
```

Train `traforest` from `rmmodeldata`:

```{r}
set.seed(290875)
tf_cmod_wd = rmmodeldata::traforest(m, formula = y ~ horTh | age, control = ctrl,
  ntree = 50, mtry = 1, trace = TRUE, data = GBSG2)
```

Predict both models and compare output:

```{r}
pred_o  = predict(tf_cmod, newdata = GBSG2)
pred_wd = predict(tf_cmod_wd, newdata = GBSG2)

all.equal(pred_o, pred_wd)
```

